---
title: "Multilevel Model"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = TRUE,
                      fig.width = 10,
                      fig.height = 10,
                      dev.args = list(bg="transparent"))

library(tidyverse)
require(nlme)
library(here)
library(rio)

data <- import(here("data", "mlm_data.csv"),
               setclass = "tbl_df") 

head(data)

saje <- import(here("data", "saje_mlm.csv"),
               setclass = "tbl_df") 

leli <- import(here("data", "leli_mlm.csv"),
               setclass = "tbl_df") 

giad <- import(here("data", "giad_mlm.csv"),
               setclass = "tbl_df") 

```

## Analysis All Participants 

### Null (unconditional) model

```{r}
d.Null <- lme(DV~1,random=~1|Case,data=data,
control=list(opt="optim"),na.action="na.omit")
coefficients(d.Null)
intervals(d.Null)
summary(d.Null)
```


### Model with random intercept and change in level (with an autocorrelation component)
```{r}
d.Level <- lme(DV~1+Phase,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
coefficients(d.Level)
intervals(d.Level)
summary(d.Level)
```


### Model with random intercept and change in slope (with an autocorrelation component)
```{r}
d.Time <- lme(DV~1+Time_CTR,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Time)
intervals(d.Time)
summary(d.Time)
```


### Model with random intercept and change in level/slope in Tx (with autocorrelation)
```{r}
d.Model <- lme(DV~1+Phase+Time_PhaseCTR,random=~1|Case,data=data,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Model)
intervals(d.Model)
summary(d.Model)
```

### Results


| **Value** | **Score** | **_p_-Value** |
| :-------- | :-------: | :-----------: |
| Autocorrelation     | .418      |  |
| Level | 6.01      | .013 |
| Slope | 3.52     |  .037    |



Interpretation: The effect size isn't particularly large, but the _p_-value is significant, which is helpful.The _p_-value for the change in slope is also significant.


## SAJE

### Null (unconditional) model

```{r}
d.Null_saje <- lme(DV~1,random=~1|Case,data=saje,
control=list(opt="optim"),na.action="na.omit")
coefficients(d.Null_saje)
#intervals(d.Null_saje)
summary(d.Null_saje)
```


### Model with random intercept and change in level (with an autocorrelation component)
```{r}
d.Level_saje <- lme(DV~1+Phase,random=~1|Case,data=saje,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
coefficients(d.Level_saje)
#intervals(d.Level_saje)
summary(d.Level_saje)
```


### Model with random intercept and change in slope (with an autocorrelation component)
```{r}
d.Time_saje <- lme(DV~1+Time_CTR,random=~1|Case,data=saje,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Time_saje)
#intervals(d.Time_saje)
summary(d.Time_saje)
```


### Model with random intercept and change in level/slope in Tx (with autocorrelation)
```{r}
d.Model_saje <- lme(DV~1+Phase+Time_PhaseCTR,random=~1|Case,data=saje,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Model_saje)
#intervals(d.Model_saje)
summary(d.Model_saje)
```

### Results


| **Value** | **Score** | **_p_-Value** |
| :-------- | :-------: | :-----------: |
| Autocorrelation     | -0.826      |  |
| Level | 76.802      | .000 |
| Slope | 9.147     |  .0068    |





## LELI

### Null (unconditional) model

```{r}
d.Null_leli <- lme(DV~1,random=~1|Case,data=leli,
control=list(opt="optim"),na.action="na.omit")
coefficients(d.Null_leli)
#intervals(d.Null_leli)
summary(d.Null_leli)
```


### Model with random intercept and change in level (with an autocorrelation component)
```{r}
d.Level_leli <- lme(DV~1+Phase,random=~1|Case,data=leli,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
coefficients(d.Level_leli)
#intervals(d.Level_leli)
summary(d.Level_leli)
```


### Model with random intercept and change in slope (with an autocorrelation component)
```{r}
d.Time_leli <- lme(DV~1+Time_CTR,random=~1|Case,data=leli,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Time_leli)
#intervals(d.Time_leli)
summary(d.Time_leli)
```


### Model with random intercept and change in level/slope in Tx (with autocorrelation)
```{r}
d.Model_leli <- lme(DV~1+Phase+Time_PhaseCTR,random=~1|Case,data=leli,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Model_leli)
#intervals(d.Model_leli)
summary(d.Model_leli)
```

### Results


| **Value** | **Score** | **_p_-Value** |
| :-------- | :-------: | :-----------: |
| Autocorrelation     | -0.243      |  |
| Level | 63.566      | .0004 |
| Slope | -13.630     |  .1593    |



## GIAD

### Null (unconditional) model

```{r}
d.Null_giad <- lme(DV~1,random=~1|Case,data=giad,
control=list(opt="optim"),na.action="na.omit")
coefficients(d.Null_giad)
#intervals(d.Null_giad)
summary(d.Null_giad)
```


### Model with random intercept and change in level (with an autocorrelation component)
```{r}
d.Level_giad <- lme(DV~1+Phase,random=~1|Case,data=giad,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
coefficients(d.Level_giad)
#intervals(d.Level_giad)
summary(d.Level_giad)
```


### Model with random intercept and change in slope (with an autocorrelation component)
```{r}
d.Time_giad <- lme(DV~1+Time_CTR,random=~1|Case,data=giad,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Time_giad)
#intervals(d.Time_giad)
summary(d.Time_giad)
```


### Model with random intercept and change in level/slope in Tx (with autocorrelation)
```{r}
d.Model_giad <- lme(DV~1+Phase+Time_PhaseCTR,random=~1|Case,data=giad,
correlation=corAR1(form=~1|Case),control=list(opt="optim"),na.action="na.omit")
# Rename variables and use only complete cases
coefficients(d.Model_giad)
#intervals(d.Model_giad)
summary(d.Model_giad)
```

### Results


| **Value** | **Score** | **_p_-Value** |
| :-------- | :-------: | :-----------: |
| Autocorrelation     | 0.991      |  |
| Level | 141.950      | .0266 |
| Slope | 28.2272     |  .3038    |