---
title: "Tau-U"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

## MLM Design Results 

| **Value** | **Score** |
| :-------- | :-------: |
| Tau-U     | .810      |
| *z*-Score | 2.94      |
| *p*-value | .0032     | 


**_Interpretation:_** A _Tau-U_ value of .810 corresponds to a medium to high treatment effect. All three participants required a baseline trend correction. 



## AB Tau-U Calculations with `SCAN` Package

Code for calculations accessible [here](https://jazznbass.github.io/scan-Book/overlapping-indices.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r setup 1, include=FALSE}
library(tidyverse)
library(rio)
library(here)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(SCVA)
library(patchwork)
library(colorblindr)
library(scan)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )
 
```


### SAJE 

#### Parker (2011) Version

```{r, include=TRUE}
saje_1 <- scdf(c(44, 35, 40, 104, 118, 122), 
               phase.design = c(A = 3, B = 3))

saje_res <- tau_u(saje_1)

print(saje_res, complete = TRUE)
```

#### Tarlow (2016) Version

This calculation is based on Kendalls Tau

```{r, include=TRUE}
saje_2 <- scdf(c(A = 44, 35, 40, B = 104, 118, 122))

corrected_tau(saje_2)
```



### LELI

#### Parker (2011) Version

```{r, include=TRUE}
leli_1 <- scdf(c(33, 54, 39, 27, 48, 125, 89, 100), phase.design = c(A = 5, B = 3))

leli_res <- tau_u(leli_1)

print(leli_res, complete = TRUE)
```

#### Tarlow (2016) Version


```{r, include=TRUE}
leli_2 <- scdf(c(A = 33, 54, 39, 27, 48, B = 125, 89, 100))

corrected_tau(leli_2)
```



### GIAD

#### Parker (2011) Version

```{r, include=TRUE}
giad_1 <- scdf(c(157, 123, 71, 94, 208, 226, 265), phase.design = c(A = 4, B = 3))

giad_res <- tau_u(giad_1)

print(giad_res, complete = TRUE)
```

#### Tarlow (2016) Version


```{r, include=TRUE}
giad_2 <- scdf(c(A = 157, 123, 71, 94, B = 208, 226, 265))

corrected_tau(giad_2)
```